### 2024-01-09 documentation/thesis/thesis_document.tex
more thesis

@@

\begin{itemize}
\tightlist
\item
  Raspberry Pi OS Lite - \passthrough{\lstinline!debian bookworm x64!},
\item
  \gls{mrp} \ref{software-readout-framework}-library - version
  \passthrough{\lstinline!1.4.1!}
\item
  Unified Sensor \ref{unified-sensor}-firmware - version
  \passthrough{\lstinline!1.0.1!}
\end{itemize}

@@

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical \passthrough{\lstinline!RS232!} interface. As with the
other sensors, this interface consists of your
\passthrough{\lstinline!RaspberryPi Pico!} with an additional level
shifter. The Teslameter is connected to the microcontroller using two
free \gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration and the protocol of the measuring device
was implemented.

@@

\hypertarget{extension-modules}{%
\section{Extension Modules}\label{extension-modules}}

Im folgenden werden die einzelnen module, welche vom user modifiziert
und ersetzt werden können im details erleutert.

\hypertarget{hal}{%
\subsection{HAL}\label{hal}}

\begin{itemize}
\tightlist
\item
  aufbau hal im grunde wird nur ein die commandos an das sensor cli
  weitergegeben
\item
  alle sensoren implementieren mehr oder weniger die gleichen befehle
\item
  hal gibt nur weiter und ist ``dumm''
\end{itemize}

\hypertarget{visualisation}{%
\subsection{Visualisation}\label{visualisation}}

\hypertarget{storage}{%
\subsection{Storage}\label{storage}}

\begin{itemize}
\tightlist
\item
  metadata management
\end{itemize}

\hypertarget{export}{%
\subsection{Export}\label{export}}

\begin{itemize}
\tightlist
\item
  format import export
\item
  matlab
\end{itemize}

@@

At the current described scenarios, it is only possible to detect and
use sensors that are directly connected to the \gls{pc} with the
\gls{mrp}-library. It has the disadvantage that there must always be a
physical connection. This can make it difficult to install multiple
sensors in measurement setups where space or cable routing options are
limited. So multibe sensor can be connected to a
\passthrough{\lstinline!remote!} \gls{pc} which is available on the
network. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
footprint and low power consumption make it a good choice. It can also
be used in a temperature chamber.

@@

\begin{itemize}
\tightlist
\item
  redirect to each capable sensor
\item
  extend commands using an id parameter
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Function description
\item
  Input parameters - using \passthrough{\lstinline!param!} and
  \passthrough{\lstinline!type!}
\item
  Return value - using \passthrough{\lstinline!returns!},
  \passthrough{\lstinline!rtype!}
\end{itemize}

>>>>

\hypertarget{charakterisation-of-permanent-magnets}{%
\subsection{Charakterisation of Permanent
Magnets}\label{charakterisation-of-permanent-magnets}}

\begin{itemize}
\item
  zeigt ansätzte einfacher magnet vermesseungen
  \cite{Wickenbrock_2021}
\item
  contruction of hallbach ringe \cite{cmr.a.20165}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Raspberry Pi OS Lite - \gls{os}
  \passthrough{\lstinline!debian bookworm x64!},
\item
  \gls{mrp} \ref{software-readout-framework}-library - Version
  \passthrough{\lstinline!1.4.1!}
\item
  Unified Sensor \ref{unified-sensor}-firmware - Version
  \passthrough{\lstinline!1.0.1!}
\end{itemize}

@@

Another option is a custom interface board between the meter and the PC.
This is a good option as many modern \gls{pc}s or \gls{sbc}s no longer
offer an physical \passthrough{\lstinline!RS232!} interface. As with the
other sensors, this interface consists of your
\passthrough{\lstinline!RaspberryPi Pico!} with an additional level
shifter. The Teslameter is connected to the microcontroller using two
free \gls{gpio}s in \gls{uart} mode. The firmware was adapted using a
separate build configuration. In order to be able to read and correctly
interpret the data from the microcontoller, the serial protocol from
table \ref{Voltcraft_GM70_serial_protocol.csv} of the sensor was
implemented in a customized version of the
\passthrough{\lstinline!CustomSensor!} class
\ref{lst:CustomSensorClass}.

@@

\begin{itemize}
\tightlist
\item
  jeder schritt nach der DAQ basiert auf dem gleichen grundtyp datentyp
\item
  meta-daten werden bei jedem weiteren schritt hinzugeügt um
  nachverfolgbarkeit zu gewärleisten
\end{itemize}

\hypertarget{modules}{%
\section{Modules}\label{modules}}

The library consists of various modules, which are divided into two
categories:

\begin{itemize}
\tightlist
\item
  Core - All modules related to measurement data management
\item
  Extensions - Contains modules for visualizations, hardware sensor
  access
\end{itemize}

An overview of these is given in the subchapters as the following. There
are also introductory examples which provide an overview of the basic
functions in the \passthrough{\lstinline!Examples!}\ref{examples}
section, as well as further examples in the online documentation.
\cite{MagneticReadoutProcessingReadTheDocs}

\hypertarget{core-modules}{%
\subsection{Core Modules}\label{core-modules}}

\hypertarget{extension-modules}{%
\subsection{Extension Modules}\label{extension-modules}}

\hypertarget{sensor-interface}{%
\subsubsection{Sensor Interface}\label{sensor-interface}}

Another collection of optional modules provided by the library is the
connection of external hardware sensors. All compatible sensors that are
compatible with the firmware developed in the
\passthrough{\lstinline!Unified Sensor!}\ref{unified-sensor} chapter are
supported here. The library provides the following sensor \gls{hal}
modules for this purpose:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPHal!} - Firmware protocol implementation
\item
  \passthrough{\lstinline!MRPHalLocal!} - \gls{usb} sensor interface
\item
  \passthrough{\lstinline!MRPHalRemote!} - Remote sensor interface
\end{itemize}

These provide functions to communicate with a connected hardware sensor
and send commands to it. To generate these and convert the received
measurement data into the appropriate format for the core modules, there
is a suitable module for each sensor type:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!MRPReadingSourceStatic!} - for 1D and 2D
  sensor such as
  \passthrough{\lstinline!1D: Single Sensor!}\ref{d-single-sensor}
\item
  \passthrough{\lstinline!MRPReadingSourceFullsphere!} - for 3D sensors
  such as \passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere}
\end{itemize}

The decision which of these modules to use is made automatically
depending on the connected hardware. For this purpose, a static function
\passthrough{\lstinline!createReadingSourceInstance!} is implemented in
the base class \passthrough{\lstinline!MRPReadingSource!}, which
automatically creates the appropriate instance based on the sensor
capabilites.

\hypertarget{visualisation}{%
\subsubsection{Visualisation}\label{visualisation}}

\hypertarget{analysis}{%
\subsubsection{Analysis}\label{analysis}}

\hypertarget{storage-and-datamanagement}{%
\section{Storage and Datamanagement}\label{storage-and-datamanagement}}

An important aspect is data import and export. On the one hand, this
allows the library to reuse and archive the measurements. On the other
hand, the focus during development was that it is also possible to use
the data in other programs. For this purpose, an open, documented export
format must be selected. Ideally, this should be human-readable and
viewable with a simple text editor. This eliminates all binary-based
formats such as the Python pickle built into Python.

Taking these points into account, the \gls{json} format was chosen. This
is human and machine readable and there is a compatible parser for
almost every programming language.

The following code snippet \ref{lst:json_export_format_example} shows
the \gls{json} structure which is generated when a measurement thatt
using the library is exported. Here you can see that by using the
\gls{json} format, all measurement points and metadata are available in
readable plain text. This means that they can also be read out in other
programs. Using serialization, the \passthrough{\lstinline!MRPReading!}
class inherited from Python-\passthrough{\lstinline!Object!} class is
serialized via an dictionary conversion step. This \gls{json} string can
then be processed directly or written to the file system as a file.

\begin{lstlisting}[caption={JSON export structure of an MRPReading based measurement}, label=lst:json_export_format_example]
{
  "time_start": "Wed Sep 20 08:50:13 2023",
  "time_end": "Wed Sep 20 08:50:13 2023",
  "additional_data": {
      "sensor_device_path": "/dev/cu.usbmodem3867315334391",
      "sensor_name": "Unified Sensor Single Sensor",
      "sensor_id": "386731533439",
      "sensor_capabilities": ["static", "axis_b", "axis_x", "axis_y", "axis_z", "axis_temp", "axis_stimestamp"],
      "configname": "calibrationtemp30.yaml",
      "runner": "cli"
  },
  "data": [{
      "value": 0.135,
      "is_valid": true,
      "id": 0,
      "temperature": 34.32
  }],
  "measurement_config": {
      "id": "525771256544952",
      "sensor_distance_radius": 40.0,
      "magnet_type": 0
  },
  "name": "calibrationtemp30",
}
\end{lstlisting}

The exported example \ref{lst:json_export_format_example} contains the
following different object keys, which contain the following
information:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!additional\_data!} - Additional user-defined
  metadata
\item
  \passthrough{\lstinline!data!} - Measured values with value and
  measured value \gls{id}
\item
  \passthrough{\lstinline!measurement\_config!} - Information about the
  sensor used for measurement
\end{itemize}

In addition, further custom objects can be inserted into the \gls{json}
using the functions provided.

Since there are popular data processing frameworks such as
Numpy\cite{harris2020array}, or the program for mathematical
calculations, Matlab are often used, the library also supports export
formats for these systems.

The different formats can be triggered by the user by calling up the
corresponding \passthrough{\lstinline!MRPReading!} class functions:

\begin{itemize}
\tightlist
\item
  \passthrough{\lstinline!.dump()!} - \gls{json}
\item
  \passthrough{\lstinline!.to\_numpy\_matrix()!} - Numpy-Array of
  \passthrough{\lstinline!data!} object with different options
\item
  \passthrough{\lstinline!.dump\_savemat()!} - Matlab mat-file with
  measurement values and temperatures
\end{itemize}

Currently, data re-import of an exported measurement is only supported
via the \gls{json} format, as an export using the other options (Numpy,
Matlab)loses data during the export procedure.

@@

At the current described scenarios, it is only possible to detect and
use sensors that are directly connected to the host \gls{pc}. It has the
disadvantage that there must always be a physical connection. This can
make it difficult to install multiple sensors in measurement setups
where space or cable routing options are limited. So multibe sensor can
be connected to a \passthrough{\lstinline!remote!} \gls{pc} which is
available on the network. This can be a \gls{sbc} (e.g.~a Raspberry Pi).
The small footprint and low power consumption make it a good choice. It
can also be used in a temperature chamber.

@@

\begin{itemize}
\tightlist
\item
  Redirect to each capable sensor
\item
  Extend commands using an id parameter
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Function description
\item
  Input parameters, using \passthrough{\lstinline!param!} and
  \passthrough{\lstinline!type!}
\item
  Return value, using \passthrough{\lstinline!returns!},
  \passthrough{\lstinline!rtype!}
\end{itemize}
